Summary of the things that I learned

### 2024-11-15 200-category-theory.tex
Add a remark about the classical definition of the Karoubi envelope and refer to it from Remark 2.79

\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]
  We define the category $ \overline \C $. The objects of $ \overline \C $ are tuples $ (X, f) $ with $ X: \C $, $ f: \C(X, X) $ such that $ f \cdot f = f $. The morphisms between $ (X_1, f_1) $ and $ (X_2, f_2) $ are morphisms $ g: \C(X_1, X_2) $ such that $ f_1 \cdot g \cdot f_2 = g $. This can be summarized in the following diagram:
  \begin{center}
    \begin{tikzcd}
      X_1
        \arrow["f_1"', loop, distance=2em, in=-150, out=150]
        \arrow[r, "g"] &
      X_2
        \arrow["f_2"', loop, distance=2em, in=30, out=-30]
    \end{tikzcd}
  \end{center}
  The identity morphism on $ (X, f) $ is given by $ f $ and $ \overline \C $ inherits morphism composition from $ \C $.
\end{definition}
This category is called the \iindex{Karoubi envelope}, the \textit{idempotent completion}\index{idempotent completion|see{Karoubi envelope}}, the \textit{category of retracts}\index{category of retracts|see{Karoubi envelope}}, or the \textit{Cauchy completion}\index{Cauchy completion|see{Karoubi envelope}} of $ \C $.

@@

@@

\begin{remark}\label{rem:karoubi-candidate-choice}
  As we saw in this section, there are multiple candidates for the `Karoubi envelope'. Two of these candidates are equivalent to each other, but the third is not. Therefore, we need to be careful which definition we choose, because this choice has consequences. On one hand, $ \hat \C $ is univalent, but very abstract. In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism. On the other hand, $ \overline \C $ and $ \tilde \C $ are very elementary and concrete, which sometimes helps when doing constructions. However, they are not univalent, which makes working with them complicated in a different way.
\end{remark}

>>>>

\begin{definition}[\coqident{AlgebraicTheories.FundamentalTheorem.CommonUtilities.KaroubiEnvelope}{karoubi_envelope}]\label{def:karoubi}
  We define the category $ \overline \C $. The objects of $ \overline \C $ are tuples $ (X, f) $ with $ X: \C $, $ f: \C(X, X) $ such that $ f \cdot f = f $. The morphisms between $ (X_1, f_1) $ and $ (X_2, f_2) $ are morphisms $ g: \C(X_1, X_2) $ such that $ f_1 \cdot g \cdot f_2 = g $. This can be summarized in the following diagram:
  \begin{center}
    \begin{tikzcd}
      X_1
        \arrow["f_1"', loop, distance=2em, in=-150, out=150]
        \arrow[r, "g"] &
      X_2
        \arrow["f_2"', loop, distance=2em, in=30, out=-30]
    \end{tikzcd}
  \end{center}
  The identity morphism on $ (X, f) $ is given by $ f $ and $ \overline \C $ inherits morphism composition from $ \C $.
\end{definition}
This category is called the \iindex{Karoubi envelope}, the \textit{idempotent completion}\index{idempotent completion|see{Karoubi envelope}}, the \textit{category of retracts}\index{category of retracts|see{Karoubi envelope}}, or the \textit{Cauchy completion}\index{Cauchy completion|see{Karoubi envelope}} of $ \C $.

@@

\begin{remark}\label{rem:karoubi-classical}
  The situation in classical mathematics is very similar to the situation above: We can define a category $ \bar \D $ which is defined using idempotents, a category $ \tilde \D $ which consists of presheaves with chosen retractions, and a category $ \hat \D $ which is the image of $ \tilde \D $ under the forgetful functor $ F : \hat \D \to P \C $. More specifically, $ \hat \D $ is the full subcategory of $ P \C $, which we get if we only select the presheaves $ F $ such that we can find some $ X : \C $ and some retraction $ (r, s) : F \triangleleft \yo(X) $. We again have an adjoint equivalence $ \bar \D \simeq \tilde \D $ and a fully faithful, essentially surjective functor $ F : \tilde \D \to \hat \D $.

  However, in classical mathematics we have something even stronger: unlike in univalent foundations, we can use the axiom of choice to turn the weak equivalence into an adjoint equivalence $ F : \tilde \D \xrightarrow \sim \hat \D $, choosing an object $ X : \C $ and a retraction $ (r, s) : F \triangleleft \yo(X) $ for every $ F : \tilde \D $. This means that classically, the different definitions of the Karoubi envelope all coincide.
\end{remark}

@@

\begin{remark}\label{rem:karoubi-candidate-choice}
  As we saw in this section, there are multiple candidates for the `Karoubi envelope' of a category $ \C $: $ \bar \C $ (Definition \ref{def:karoubi}), $ \tilde \C $ (Definition \ref{def:karoubi'}) and $ \hat \C $ (Definition \ref{def:karoubi''}). In classical mathematics, these are all equivalent to each other (Remark \ref{rem:karoubi-classical}), but in univalent foundations $ \hat \C $ is usually not equivalent to $ \bar \C $ and $ \tilde \C $ (Corollary \ref{cor:karoubi-candidates}).

  Therefore, we need to be careful which definition we choose, because this choice has consequences. On one hand, $ \hat \C $ is univalent, but very abstract. In this category, there are classical constructions that we cannot do, because for every object, we only have mere existence of an idempotent morphism, and because the objects of $ \hat \C $ do not form a set, we cannot use the axiom of choice to pick an idempotent morphism. On the other hand, $ \overline \C $ and $ \tilde \C $ are very elementary and concrete, which sometimes helps when doing constructions. However, they are not univalent, which makes working with them complicated in a different way.
\end{remark}
